---
output:
  md_document:
    variant: markdown_github
---

# Purpose

Illustrate workthrough of Question 3: Loans and Credit.

```{r}

rm(list = ls())
gc()
library(tidyverse)

# run_project.R sources every function in code/ (one file, one function),
# loads and cleans the loan book, runs every heuristic test, the borrower
# risk profiles, the Texas deep-dive, the DTI threshold scenarios, the
# grading-system evaluation and the full default model - and saves every
# resulting table to Question3_files/tables/ and every figure to
# Question3_files/figures/.
source("run_project.R")

```

## Institute Heuristic 1: Home ownership

```{r}
home_summary
Homeownership_Default_Plot(home_summary)
```

## Institute Heuristic 3: State-level default culture (flagship map)

```{r, fig.width=10, fig.height=7}
State_Default_Map(state_summary)
```

Texas in national context:

```{r}
texas_summary
Texas_Comparison_Plot(texas_summary)
```

## Institute Heuristic 4: Does the grading system hold up for young borrowers?

```{r}
grade_age_summary
grade_monotonic
```

## DTI policy thresholds

```{r}
dti_scen
```

## Grading-system efficacy

```{r}
grade_summary
grade_auc
Grade_Default_Plot(grade_summary, grade_auc$auc)
```

## Strongest predictors of default

```{r, fig.width=10, fig.height=8}
var_importance
Risk_Driver_Plot(var_importance)
```

See `Question3.Rmd` for the full Director-facing write-up, and
`Question3_files/tables/` and `Question3_files/figures/` for every
persisted result this script produces.
