---
title: "Netflix Content Analysis: What Works in Streaming?"
author: "29418100"
date: "`r Sys.Date()`"
bibliography: Tex/ref.bib
output:
  pagedown::html_paged:
    css: ["Template/default-fonts-Texevier.css",
          "Template/default-page-Texevier.css",
          "Template/default-Texevier.css"]
    csl: Template/harvard-stellenbosch-university.csl
    template: ["Template/paged-Texevier.html"]
    toc: true
    self_contained: TRUE
abstract: |
  This concise report analyses Netflix title and movie data (up to 2023) to guide
  investors considering a new streaming service launch. Key findings: Drama and Comedy
  dominate the catalogue; US content is most numerous but Korean and Japanese titles
  score highest per-viewer; TV shows outscore movies on average TMDb ratings; and
  documentary content represents an underserved high-rating niche.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width  = 9,
  fig.height = 5
)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, scales, knitr, janitor, tidytext, forcats, pagedown)

list.files("code/", full.names = TRUE, recursive = TRUE) %>%
  as.list() %>%
  purrr::walk(~source(.))

# Load data
titles      <- readRDS("data/netflix/titles.rds")
credits     <- readRDS("data/netflix/credits.rds")
movie_info  <- readr::read_csv("data/netflix/netflix_movies.csv",
                                show_col_types = FALSE)
```

# 1. Catalogue Overview

```{r overview}
tibble::tibble(
  Metric = c("Total titles", "Movies", "TV Shows",
             "Countries represented", "Year range",
             "Avg TMDb score"),
  Value  = c(
    format(nrow(titles), big.mark = ","),
    format(sum(titles$type == "MOVIE",   na.rm = TRUE), big.mark = ","),
    format(sum(titles$type == "SHOW",    na.rm = TRUE), big.mark = ","),
    dplyr::n_distinct(
      unlist(stringr::str_split(titles$production_countries, ",")), na.rm = TRUE
    ),
    paste(min(titles$release_year, na.rm = TRUE), "–",
          max(titles$release_year, na.rm = TRUE)),
    round(mean(titles$tmdb_score, na.rm = TRUE), 2)
  )
) %>% knitr::kable(caption = "Netflix Catalogue at a Glance")
```

---

# 2. Content Growth Over Time

```{r releases, fig.cap="Netflix title releases by year — rapid growth from 2015"}
plot_releases_over_time(titles)
```

- Netflix content exploded from **2015 onward** — relevant baseline for a new entrant
- **TV shows have grown faster** than movies since 2017

---

# 3. Genre Landscape

```{r genres, fig.cap="Top 12 genres — colour shows average audience score"}
plot_genre_popularity(titles, top_n = 12)
```

- **Drama** and **Comedy** are by far the most common genres
- **Documentaries** and **Crime** achieve some of the highest average TMDb scores despite
  smaller catalogue share — an **underserved high-quality niche**

---

# 4. Rating Comparison: Movies vs. TV Shows

```{r score-dist, fig.cap="TV shows score higher than movies on average"}
plot_score_distribution(titles)
```

- TV shows have a **higher median TMDb score** and narrower distribution
- Movies have a **longer left tail** — many low-scoring titles drag the average down
- **Implication:** Investing in quality serialised content likely yields better audience scores

---

# 5. Country Breakdown — Runtime & Volume

```{r runtime, fig.cap="Median runtime by country (titles.rds, min. 5 titles)"}
# runtime lives in titles.rds; production_countries used for country label
plot_runtime_by_country(titles, top_n = 12)
```

```{r top-countries}
# netflix_movies.csv has an explicit country column — use it for volume ranking
movie_info %>%
  dplyr::filter(!is.na(country), country != "") %>%
  tidyr::separate_rows(country, sep = ",") %>%
  dplyr::mutate(country = stringr::str_trim(country)) %>%
  dplyr::count(country, sort = TRUE) %>%
  dplyr::slice_head(n = 10) %>%
  knitr::kable(col.names = c("Country", "# Movies"),
               caption = "Top 10 Countries by Movie Count (netflix_movies.csv)")
```

- **US** dominates in volume; **India** second
- **Japanese** and **Korean** films have distinctive runtimes reflecting cultural preferences
- A new streaming service could differentiate by **curating non-US content** with high scores

---

# 6. Textual Analysis — Description Keywords

```{r text-analysis, fig.cap="Most common meaningful words in Netflix title descriptions"}
if ("description" %in% names(titles)) {
  titles %>%
    dplyr::filter(!is.na(description)) %>%
    tidytext::unnest_tokens(word, description) %>%
    dplyr::anti_join(tidytext::stop_words, by = "word") %>%
    dplyr::filter(nchar(word) > 3) %>%
    dplyr::count(word, sort = TRUE) %>%
    dplyr::slice_head(n = 20) %>%
    dplyr::mutate(word = forcats::fct_reorder(word, n)) %>%
    ggplot2::ggplot(ggplot2::aes(x = word, y = n)) +
    ggplot2::geom_col(fill = "#e50914") +
    ggplot2::coord_flip() +
    ggplot2::labs(title = "Top Words in Netflix Title Descriptions",
                  x = NULL, y = "Frequency") +
    ggplot2::theme_minimal(base_size = 13)
} else {
  cat("Description column not found — check column names.")
}
```

---

# 7. Summary & Investor Recommendations

| Dimension | Finding | Recommendation |
|---|---|---|
| **Genre** | Drama/Comedy dominate; Docs punch above their weight | Lead with Drama; invest in Documentary as a differentiator |
| **Format** | TV shows score higher | Prioritise original serialised content |
| **Geography** | US has volume; Asia has quality | Blend US originals with Korean/Japanese co-productions |
| **Runtime** | Varies significantly by country | Avoid one-size-fits-all commissioning targets |
| **Growth** | Post-2015 explosion | Entering now requires quality differentiation, not volume |

> **Bottom line:** A new streaming service should invest in **high-quality TV dramas, documentary content, and Asian co-productions** rather than competing on raw volume with Netflix.
